---
title: "What went wrong?"
author: "Robert Gruener"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = city, y = hwy, color = "blue")) %>% 
  geom_point()

```

As the error message suggest, "+" should be used instead of "%>%", and the grammar of ggplot aesthetic is used in a wrong way. Moreover, the vector in which the information of city is stored was named "cty" instead of "city". The modified codes are as follows:
```{r}
data(mpg)

ggplot(mpg, aes(cty, hwy))+
  geom_point()
```


### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

```
The points are not blue because the color attribute was not called in the right way. It should not be used in the aes() function.
```{r}
ggplot(mpg, aes(displ, hwy))+
  geom_point(color = 'blue')
```
See, now the points are blue.


### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?
```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 2) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = c(5, 40))

```
Alpha is a geom element used to control opacity, so the legal value of alpha ranges from 0 (transparent) to 1 (opaque). Another geom element, size, could be adjusted to make the points slightly bigger.
```{r}
GF3 = ggplot(mpg, aes(displ, hwy, color = class)) + 
        geom_point(size = 2)
GF3
```

To change the position of the figure legend, the theme element "legend.position" has to be modified. However, "c(0,0)" and "c(1,1)" correspond to the lower-left and upper-right corners, respectively. Therefore "c(5,40)" is not the right way to position the legend box. The title can be removed using "element_blank()"
```{r}
GF3 + theme(legend.position = c(0.6, 0.75), legend.title = element_blank())
```
The legend box can be fully removed if the legend.position is set as "none".
```{r}
GF3 + theme(legend.position = "none")
```


### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```
Unless otherwise specified, geom_smooth uses inherited mappings from above. In this case, only the relationship between "displ" and "hwy" is wanted, so a new mapping has to be supplied.


```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(mapping = aes(x = displ, y = hwy), inherit.aes = F, se = F, color = 'black') #se = F makes it so it won't show the error in the line of fit
```
It's worth mentioning that I changed the color of the curve, since the original one was blue and was kind of confusing when there are already blue points.

### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

Also, the x-axis labels were overlaping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?


```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45))
```
By setting "fill" element, the box can be plotted as one color. As for the overlapping issue, the easiest way is to lower down the text angle to a proper value.

```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, fill = manufacturer, color = manufacturer)) + 
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 18))
```

