---
title: "HW02_B_Graph-Mimic"
author: "Xingruo Zhang"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load libraries, echo = TRUE, include=TRUE}
library("ggplot2")
library("magrittr") #so I can do some piping
data("diamonds")
data("mpg")
data("iris")
theme_set(theme_bw()) #I'll give you this one, you can set the theme individually for graphs
#or you can set the theme for all the graphs using theme_set()
#theme_bw() is best theme (IMO)

#for graph 3:
library("ggrepel")
```

## HW02 Part B

For this part of the HW, the goal is to try to recreate the graphs I make from scratch. I will only provide the MD, not the actual code I used to create it besides which data I use to create it. The rest will be up to you. 

Try for all 4, but if you are struggling don't worry about it. Try your best for each, if you don't get everything that's what the peer-review is for. :smile:


### Graph 1
```{r, echo = T, include = TRUE}
data("diamonds")
#hint think about the *position* the bars are in...
```


Using the diamonds dataset, make this graph:
```{r graph1 code, echo=FALSE}
p1 <- ggplot(diamonds, aes(x = cut, fill = clarity)) +
  # Make bars for each cut side by side
  geom_bar(position = "dodge") +
  # Add titles and axis labels
  labs(title = "My Diamond Collection", subtitle = "Boxplot representing the number of diamonds in my diamond collection by \ntype of cut quality and clarity of diamond", x = "Diamond Cut", y = "Number of Diamonds") + 
  # Center the titles
  theme(plot.title = element_text(hjust = 0.5)) +
  # Text annotation for diamonds with ideal cut
  annotate("text", x = 4, y = 4500, label = "My Best Diamonds, \n of course") +
  # Rectangular box to highlight diamonds with ideal cut 
  annotate("rect", xmin = 4.5, xmax = 5.5, ymin = 0, ymax = 5000, alpha = 0.3)

p1
```

### Graph 2
```{r, echo = T, include = TRUE}
data("iris")
```

Using the iris dataset, make this graph:
```{r graph 2 code, echo=FALSE}
p2 <- ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) +
  # Add the point layer to the plot, and specify shapes by species
  geom_point(aes(shape = Species)) + 
  # Wrap the plots for the three species to be three horizontally parallel graphs, and adjust the vertical scale for each plot 
  facet_wrap(. ~Species, scales = "free_y") + 
  # Add the regression lines, turn off the standard errors, change line color to black, and make lines to be thinner
  geom_smooth(method = 'lm', se = FALSE, color = "black", size = 0.5)

p2
```


### Graph 3
You'll need the information in this first box to create the graph
```{r, echo = TRUE}
data("mpg")
corvette <- mpg[mpg$model == "corvette",]
#install
require("ggrepel") #useful for making text annotations better, hint hint
set.seed(42)
```

Now using the mpg dataset and the corvette dataset, make this graph:

```{r graoh 3 code}
p3 <- ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  # Add an extra layer of points using the corvette dataset
  geom_point(aes(x = displ, y = hwy), corvette, color = "blue") +
  # Add the plot title
  labs(title = "Corvettes are a bit of an outlier") + 
  # Bolden the plot title
  theme(plot.title = element_text(face = "bold")) + 
  # Add annotations for the corvette data points
  geom_text_repel(aes(x = displ, y = hwy, label = paste0("Corvette, ", year)), corvette)

p3
```

There is a trick to getting the model and year to print off together. `paste()` is a useful function for this, also pasting together parts of file names and parts of urls together. 


### Graph 4 
```{r, echo = T}
data(mpg)

#hint for the coloring, colorbrewer and you can set palette colors and make your graphs colorblind friendly
library(RColorBrewer)
display.brewer.all(colorblindFriendly = T) #take a look at the colorblindfriendly options
```

The above graph lets you see some colobrlind friendly palettes. For the graph below, I used Set2.



Now using the above mpg dataset, make this graph


```{r graph 4 code}
p4 <- ggplot(mpg, aes(x = class, y = cty)) +
  # Add the layer of jittered points and color by class
  geom_point(aes (color = class), position  = position_jitter()) +
  # Add the layer of boxplots, set the boxplots to be transparent, and hide the outliers
  geom_boxplot(fill = NA, outlier.shape = NA) +
  # Flip the coordinates to make the boxplots horizontal
  coord_flip() + 
  # Add the title and the axis labels
  labs(x = "Car Class", y = "City mpg", title = "Horizontal BoxPlot of City MPG and Car Class") +
  # Change the color of the jittered points
  scale_color_brewer(palette = "Set2")

p4

# I have a question here: are the axis labels in the sample graph in the wrong positions?
```




