---
title: "What went wrong?"
author: "Robert Gruener"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = cty, y = hwy, color = "blue")) +
  geom_point()

#issue: used %>% instead of plus at the end of line 36, also "city" needs to be "cty"
```

### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) + 
  geom_point(color = "blue")

#issue: The aestetics should be in the ggplot function on line 45, without the color included here. The color needs to be included in geom_point() in order to be recognized as an attribute and not an aesthetic. 
```



### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?
```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 2, size = 2.5) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = c(.6, .8)) +
  theme(legend.title = element_blank())

#mistake number 1: alpha can only go from 0 to 1 with 1 being totally opaque, so setting it to 2 does not make any difference. Instead, you should have changed the size of the points, for example in the code above I changed size to 2.5 

#mistake number 2: you can not directly put the ordered pair into the function, as these values do not refer to the values on the graph. The range for legend position is (0,0) being bottom lefthand corner to (1,1) being the top right hand corner. You can guesstimate the values based off of this, and then continue to toggle with these values until you're satisfied with the location. 

#To remove legend title "class": theme(legend.title = element_blank())

#To remove plot legend completely: change legend.position = "none" in the code above. 
```

### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```

### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

Also, the x-axis labels were overlaping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?


```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer, fill = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = .5))

#Issue: color changes the outline only, so you also need to set the fill to manufacturer to reach the desired look. Also, when you rotate it makes the middle of the axis label aligned at the edge, so you must used vjust=value and hjust=value to specify. 
```



