---
title: "HW02_B_Graph-Mimic"
author: "Sherzod Tokamov"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load libraries, echo = TRUE, include=TRUE}
library(ggplot2)
library(magrittr) #so I can do some piping
data(diamonds)
data(mpg)
data(iris)
theme_set(theme_bw()) #I'll give you this one, you can set the theme individually for graphs
#or you can set the theme for all the graphs using theme_set()
#theme_bw() is best theme (IMO)

#for graph 3:
library(ggrepel)


```

## HW02 Part B

For this part of the HW, the goal is to try to recreate the graphs I make from scratch. I will only provide the MD, not the actual code I used to create it besides which data I use to create it. The rest will be up to you. 

Try for all 4, but if you are struggling don't worry about it. Try your best for each, if you don't get everything that's what the peer-review is for. :smile:


### Graph 1
```{r, echo = T, include = TRUE}
data("diamonds")
#hint think about the *position* the bars are in...
```


Using the diamonds dataset, make this graph:
```{r graph1 code, echo=FALSE}
#Create a bar graph using geom_bar and specify position="dodge" to have bars side by side.
ggplot(diamonds, aes(x=cut, fill = clarity)) +
    geom_bar(stat="count", position = "dodge") +
    annotate("rect", xmin = 4.5, xmax= 5.5, ymin=0, ymax = 5000, alpha=0.2) + #this is to add a shaded rectangle
    annotate("text", label = "My Best Diamonds,\nof course", x = 4, y = 4500)+ #this is to add the text 
    labs(x="Diamond Cut", y = "Number of Diamonds", title = "My Diamond Collection", subtitle = "Boxplot representing the number of diamonds in my diamond collection \nby type of cut quality and clarity of diamond") + #adds labels to the plot
    theme(plot.title = element_text(hjust = 0.5, face = "bold")) #this centers the title

```

### Graph 2
```{r, echo = T, include = TRUE}
data(iris)
```

Using the iris dataset, make this graph:
```{r graph 2 code, echo=FALSE}
combined_plot <- ggplot(iris, aes(Sepal.Length, Petal.Length, color = Species, shape = Species)) +
  geom_point() + #up to this step, R will produce a combined plot of all species
  geom_smooth(method = "lm", se = FALSE, color = "black") #this will add linear fit with no errors
combined_plot + facet_wrap(. ~ Species, scales = "free_y") #now we can separate the plot by species using facet_grid with formula x~y. I'm putting . for x and Species for y to have the dividing lines parallel to y-axis

```


### Graph 3
You'll need the information in this first box to create the graph
```{r, echo = TRUE}
data("mpg")
corvette <- mpg[mpg$model == "corvette",]
#install
require("ggrepel") #useful for making text annotations better, hint hint
set.seed(42)
```

Now using the mpg dataset and the corvette dataset, make this graph:

```{r graoh 3 code}
ggplot(mpg, aes(displ, hwy)) +
  geom_point() +
  geom_point(data = corvette, aes(displ, hwy), color = "blue") + #highlight only the corvette datapoints in blue
  geom_text_repel(data = corvette, label = paste("Corvette,", corvette$year)) + #Label the highlighted datapoints using paste function.
  labs(title = "Corvettes are a bit of an outlier") + #Add plot title
  theme(plot.title = element_text(face = "bold")) + #make plot title bold
  expand_limits(x=1:8)

```

There is a trick to getting the model and year to print off together. `paste()` is a useful function for this, also pasting together parts of file names and parts of urls together. 


### Graph 4 
```{r, echo = T}
data(mpg)

#hint for the coloring, colorbrewer and you can set palette colors and make your graphs colorblind friendly
library(RColorBrewer)
display.brewer.all(colorblindFriendly = T) #take a look at the colorblindfriendly options
```

The above graph lets you see some colobrlind friendly palettes. For the graph below, I used Set2.



Now using the above mpg dataset, make this graph

```{r graph 4 code}

```




