---
title: "What went wrong?"
author: "Ben Wang"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = cty, y = hwy, color = "blue")) +
  geom_point()
```
### In the tutorial on DataCamp, we always used '+' for geom_point functions so I tried that here
### I tried running the program but it could not find the object 'city'. The data refers to it as 'cty' instead of 'city', so I changed 'city' to 'cty'
### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(
```{r}
ggplot(data = mpg, aes(x = displ, y = hwy)) + 
  geom_point(color = "blue")

```
### Need to have color separately in 'geom_point()'


### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?
```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 2) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = c(0.65, 0.85)) +
  theme(legend.title = element_blank())

```
### Alpha does not change the size, it changes the opacity (0 is transparent, 1 is opaque). We change 'alpha' to 'size' to set size 
### Experimented with different coordinates until I got the legend where I wanted it
### Removing legend title wouldn't let us use "none" so "element_blank" worked instead. To completely hide the legend, I could give it a position not seen in the graph (legend.position = c(10000,10000)) or use "none".

### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy)) + 
  geom_point(aes(color = drv)) + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```
### color = drv is responsible for drawing the lines. Since it was inside ggplot(mapping), the lines were drawn indepedently of geom_point and geom_smooth layers. Placing it only in geom_point draws the line according to the point layer only, creating one line for the general relationship.

### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

Also, the x-axis labels were overlapping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?


```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, fill = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
### 'color' changes outline, 'fill' changes actually inside of the box
### use 'hjust' to adjust horizontal axis distance

