---
title: "HW02_B_Graph-Mimic"
author: "YOUR NAME HERE"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r load libraries, echo = TRUE, include=TRUE}
library("ggplot2")
library("magrittr") #so I can do some piping
data("diamonds")
data("mpg")
data("iris")
theme_set(theme_bw()) #I'll give you this one, you can set the theme individually for graphs
#or you can set the theme for all the graphs using theme_set()
#theme_bw() is best theme (IMO)

#for graph 3:
library("ggrepel")


```

## HW02 Part B

For this part of the HW, the goal is to try to recreate the graphs I make from scratch. I will only provide the MD, not the actual code I used to create it besides which data I use to create it. The rest will be up to you. 

Try for all 4, but if you are struggling don't worry about it. Try your best for each, if you don't get everything that's what the peer-review is for. :smile:


### Graph 1
```{r, echo = T, include = TRUE}
data("diamonds")
#hint think about the *position* the bars are in...
```


Using the diamonds dataset, make this graph:
```{r graph1 code, echo=FALSE}
ggplot(diamonds, aes(cut, color = clarity, fill = clarity)) + #plot cut, color/fill based on clarity
  geom_bar(position = "dodge") + #write bars, dodged
  labs(x = "Diamond Cut", y = "Number of Diamonds", title = "My Diamond Collection", subtitle = "Boxplot representing the number of diamonds in my diamond collection by\ntype of cut quality and clarity of diamond") + #add all labels
  theme(plot.title = element_text(hjust = 0.5)) + #center title
  annotate("text", x = 4, y = 4500, label = "My Best Diamonds,\nof course") + #add caption
  annotate("rect", xmin = 4.5, xmax = 5.5, ymin = 0, ymax = 5000, alpha = 0.4) #add highlight rect
  




```

### Graph 2
```{r, echo = T, include = TRUE}
data("iris")
```

Using the iris dataset, make this graph:
```{r graph 2 code, echo=FALSE}
iris$SpeciesOrdered <- factor(iris$Species, levels = c("versicolor", "setosa","virginica")) #good order

iris_plot <- ggplot(iris, aes(Sepal.Length, Petal.Length,color = Species, shape = Species))

iris_plot + facet_wrap(vars(SpeciesOrdered),scales = "free") + #make three subplots
  scale_color_manual(values = c("green","red","dodgerblue2")) + #specify colors
  scale_shape_manual(values = c(17, 16, 15)) + #specify shapes
  scale_x_continuous(limits = c(4.2, 8)) + #set xlim
  geom_point() + #plot points
  geom_smooth(method = "lm", se = F, color = "black") #plot trend line

```


### Graph 3
You'll need the information in this first box to create the graph
```{r, echo = TRUE}
data("mpg")
corvette <- mpg[mpg$model == "corvette",]
#install
require("ggrepel") #useful for making text annotations better, hint hint
set.seed(42)
```

Now using the mpg dataset and the corvette dataset, make this graph:

```{r graoh 3 code}

ggplot(corvette, aes(displ,hwy,label = paste("Corvette,",year))) + #plot corvette data
  labs(title = "Corvettes are a bit of an outlier") + #add title
  geom_point(color = "blue") + #corvettes are blue
  geom_text_repel() + #add corvette text
  geom_point(data = mpg[mpg$model != "corvette",], color = "black") + #plot all other data
  scale_x_continuous(breaks = c(1:8), limit = c(1,8)) #set xlim and x breaks
  


```

There is a trick to getting the model and year to print off together. `paste()` is a useful function for this, also pasting together parts of file names and parts of urls together. 


### Graph 4 
```{r, echo = T}
data(mpg)

#hint for the coloring, colorbrewer and you can set palette colors and make your graphs colorblind friendly
library(RColorBrewer)
display.brewer.all(colorblindFriendly = T) #take a look at the colorblindfriendly options
```

The above graph lets you see some colobrlind friendly palettes. For the graph below, I used Set2.



Now using the above mpg dataset, make this graph

```{r graph 4 code}

ggplot(mpg,aes(class,cty)) + #plot class and city
  labs(title = "Horizontal BoxPlot of City MPG and Car Class", y = "Car Class", x = "City mpg") + #text
  geom_boxplot(outlier.shape = NA) + #boxplot, outliers removed
  coord_flip() + #make horizontal
  geom_point(aes(color = class), position = position_jitter(width = 0.3, height = 0)) + #points w jit
  scale_y_continuous(breaks = seq(10, 35, by=5),limit = c(10,35)) + #set ylim & y breaks
  theme(panel.grid = element_blank()) + #remove grid
  theme(panel.border = element_blank()) + #remove border
  theme(axis.line = element_line(color = "black")) + #keep axes, in black
  scale_color_brewer(palette = "Set2") #set color palette to Set2




```




