---
title: "What went wrong?"
author: "Robert Gruener"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = city, y = hwy , color = "blue")) + 
  geom_point()

```
The initial error was the %% connecting the ggplot() and the geom_point() functions. After I changed the %% to a +, I keep getting an error message saying city is not found. I look at the column headings in the dataset, city is labeled as cty, and still I cannot get the plot to show up (despite changing the x-axis to "x = cty) I am leaving this alone. - DS


### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

```
I've made the color equal the hexadecimal system R uses for color. I used 000000, even though I believe that is black. But it looks blue here. I am not sure why the color argument is the name of the legend. but yolo.- DS

Now I see, I had the color assignment within aesthetics. to assign color, it needs to be outside of that function. I have since corrected it. - DS


### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?
```{r}
p <- mpg %>% 
 ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 2, size = 2) 

q <- p + theme(legend.position = c(0.6, 0.85)) + theme(legend.direction = "horizontal")

##Removing the legend title
q + theme(legend.title = element_blank())

##Removing the plot legend
## q + theme(legend.position = 'none')
```
I added the new size argument within aesthetics function (size=2). This caused the dots to be larger. To help with the legends, I have assigne the ggplot function to p. Secondly, I added theme, legend position to top, and the graph generate has the legend on the top of the graph. Changing to a c() vector makes the legend disappear. 

AHHHH ok so coordinates need to be 0 < c < 1. My b. 

Correctly coded for legened modicifcations. Assigned newly positioned legend to q and modified the next two steps using q. Simply remove ## from last bit of code to run program. - DS



### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy)) + 
  geom_point() + geom_smooth() #se = F makes it so it won't show the error in the line of fit


```

I may have taken the easy way out. I tried to look online on how to specify. I thought I had figured out it by specifying aesthetic command in geom_smooth (I had written, geom_smooth(aes(x = displ, y = hwy)) thinking that it would plot against only those coordinates. but to no avail). The last resot option I could think of was to eliminate the color assignment, and now only one line is present. -DS


### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

Also, the x-axis labels were overlaping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?


```{r}
v <- ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer, fill = manufacturer)) + 
  geom_boxplot() + theme(axis.text.x = element_text(angle = 45)) + theme(axis.text.x = element_text(hjust = 1))

v
```

##Awesome, first attempt. I assigned fill = manufacturarer to fill in the boxes in the boxplot. 

After some digging, looked in the "element_text()" function. I saw angle, I played with lineheight (my answer from an initial google, but values of -3, 0, 7 in lineheight provided no changes in the car names in the graph). Then I tried hjust and used 1 as my first guess. 
The graph looks clean - DS

