---
title: "What went wrong?"
author: "Robert Gruener"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = city, y = hwy, color = "blue")) %>%
  geom_point()

```

# CORRECTED CODE for Graph 1

```{r}
data(mpg)

ggplot(mpg,aes(cty,hwy,color = "blue"))+
  geom_point()
```


### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

```

#CORRECTED CODE for Graph 2
```{r}
ggplot(mpg,aes(displ,hwy))+
  geom_point(color="blue")
```


### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

#ANSWER for Graph 3 - 1st mistake
Alpha is an argument that controls the opacity of the points so setting it to 2 will make the points appear at 20% transparency. To make the points slightly bigger, I would use size instead of alpha. 

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?

#ANSWER for Graph 3 - 2nd mistake
To change the legend position to the top of the graph, I can simply insert the argument value "top" in the function theme such that the code would read theme(legend.position="top"). 

Another way to do this is to use a numeric vector c(x,y) as an argument in the function theme, especially if I have a very specific location where I would like the legend to appear. However, the values can only be between 0 and 1 in which c(0,0) corresponds to "bottom left" and c(1,1) corresponds to "top right". In the codes for this graph fail, the values was set to be bigger than 1 and instantly, we know that is a mistake. In this case where this person wanted to move the legend to top of the graph such that it is at approximately the point/ordered pair (5,40), he can try code theme(legend.position = c(0.60, 0.80)) and adjust it accordingly from there.

To remove the legend title ("class"), code theme(legend.title = element_blank())

To remove the plot legend completely, code theme(legend.position="none")
```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 2) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = c(5, 40))

```
#CORRECTED CODE for Graph 3
```{r}
mpg%>%
ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 3) +
  theme(legend.direction = "horizontal") +
  theme(legend.position = c(0.60, 0.80)) + 
  theme(legend.title = element_blank()) #to remove legend title if desired

#To remove plot legend completely
mpg%>%
ggplot() +
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 3) +
  theme(legend.direction = "horizontal") +
  theme(legend.position = "none")
```

### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```
#CORRECTED CODE for Graph 4
This person is getting 3 lines because the variable drv was assigned to a color aesthetic (showing different colors) and since there were three categories, R creates 3 lines, one for each category instead of just one line that shows the general relationship. 

At first, I wasn't sure how exactly I can correct this but I found a post on stackoverflow that was really helpful!

So there are two ways to solve this problem:

1) Override the color aesthetic in geom_smooth layer
```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F, color = "black") #se = F makes it so it won't show the error in the line of fit
```
2) Move the color aesthetic only to layer(s) that need it
```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy)) + 
  geom_point(aes(color = drv)) + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```

### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

Also, the x-axis labels were overlaping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?


```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45))
```
#CORRECTED CODE for Graph 5
To make the box one color instead of just the outline, use fill instead of color. 

To adjust the x-axis labels such that they aren't on the graph, use margin. I initially tried using vjust such that my code read theme(axis.title.x = element_text(vjust = -.05)) but I saw no results. I then stumbled upon someone commenting on a stackoverflow post that since ggplot2, the vjust parameter has been superceded by margins and that is a better way to move text around. Just fyi, margins can be specified for top (t), right (r), bottom (b) and left (l) to position text vertically and horizontally. 

```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, fill = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, margin = margin(t = 10))) 
  #theme(axis.title.x = element_text(margin = margin(t = 20))) -> I played around with margin and realized that my original code moved the legend title, not the axis labels. I am just commenting it out here so that it will remind me of the thought process I went through to achieve the desired results!
```



