---
title: "What went wrong?"
author: "Robert Gruener"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r Troubleshooting Pipes}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = cty, y = hwy, color = "blue")) + 
  geom_point()

# %>% needed to be + AND object 'city' does not exist in mpg
```

### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(
```{r Changing Color of Points}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(color = "blue")
#When data and aes are group with color, color changes based on group. 
#E.g. color = manufacturer would change data color by each manufacturer
```



### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger?

-Alpha affects the opacity of a geom. Values range from 0 to 1, with lower values having higher transparency. Setting this value to 2 should do nothing, because it is outside the range of values. Size can be used to change the size of points.

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?

-Use legend.position with a two-element numeric vector to shift legend position inside of plot. Remove legend title with legend.title = element_blank(). Remove legend completely by setting legend.position to none.
```{r Legend Position Shifted}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 2) + 
  theme(legend.direction = "horizontal",
        legend.position = c(0.63, 0.85), #Sets legend to 63% right, and 85% top
        legend.title = element_blank(), #Removes title from legend
        )

#Plot without a legend
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 2) + 
  theme(legend.position = "none")
```

### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

-There are three lines initially fit because the data is separated into three groups by colour = drv. In order to have a single line of fit, set grouping aesthetic to 1.
```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(aes(group = 1), se = F) #se = F makes it so it won't show the error in the line of fit
```

### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

-In order to change the boxplot color, alter the boxplot layer. Setting color in ggplot changes color based on group, it does not set the plot to a single color.

Also, the x-axis labels were overlapping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?

-Use vjust in element_text to alter the vertical justification of the x-axis text.
```{r Color changing and x axis tex}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer)) + 
  geom_boxplot(color = "#00AFBB") + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6)) #vjust changes vertical justification.
```



