---
title: "What went wrong?"
author: "Robert Gruener"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

_The error says mapping must be created by aes() and %>% should be +. %>% was changed._
_Changed "city" to "cty" when "city" could not be found._

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = cty, y = hwy, color = "blue")) + 
  geom_point()

```

### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(

_Color had to be removed from within aes()._

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

```



### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

_Alpha sets element transparency; setting it higher (within a range of 0 - 1) increases the opacity of the points._
_To increase point size, add "size = <size wanted>" within the point geometry function._

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?

_To move the legend, add the specified points as if the plot x and y axes maximums were 1._
_To remove the legend title, set legend.position = a blank element._
_To remove the plot legend completely, set legend.position within theme() equal to "none"._

```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 1, size = 2.5) +
  theme(legend.direction =  "horizontal") +
  theme(legend.position = c(.66, .8)) +
  theme(legend.title = element_blank())
  

```

### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

_The layer that divided up the colors by drv should have been placed in the geom-point(), because placing it in ggplot places it on a more "upstream" layer upon which geom-smooth() acted._

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy)) + 
  geom_point(aes(color = drv)) + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```

### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

_Used "fill" to color the inside of the boxes as well. Removed the legend because it seemed redundant with the x axis._

Also, the x-axis labels were overlaping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?

_Added a margin with whitespace at the top to avoid overlap._

```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer, fill = manufacturer)) + 
  geom_boxplot() + 
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 45, margin = margin(13, 0, 0, 0, "pt")))
  
```



