---
title: "What Went Wrong?"
author: "Olivia Pura"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```


## Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = city, y = hwy, color = "blue")) %>% 
  geom_point()

```

**The code _pipes_ the first layer of the graph into the `geom_point()` layer, rather than adding the `geom_point()` layer to the graph with a `+`.**

### Corrected Graph 1


```{r}
data(mpg) #this is a dataset from the ggplot2 package

ggplot(data = mpg, mapping = aes(x = cty, y = hwy, color = "blue")) +
  geom_point()

```

## Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

```

**To set the color of a `geom_point()` layer, the `color` attribute must be placed _outside_ of the `aes()`. Otherwise, it suggests that the `color` attribute is converying information about a variable.**

### Corrected Graph 2
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

```

## Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

**Setting the `alpha` to 2 causes an error, and R is unable to generate the graph. `alpha` determines the opacity of the point. If you wanted the points slightly bigger, you can set the `size` aesthetic as an argument in the `geom_point()` function.**

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?

**To move the legend, you would use `theme(legend.position = c(x, y))`, where `x` and `y` are values between 0 and 1. (0,0) corresponds to the bottom-left corner of the graph, while (1,1) corresponds to the top right corner. To remove the legend title, you add a layer containing `theme(legend.title = element_blank())`. Finally, to remove the legend completely, you can add a layer containing `theme(legend.position = "none")`.**

### Corrected Graph 3

```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 2) +
  theme(legend.direction = "horizontal") +
  theme(legend.position = c(0.65, 0.84)) +
  theme(legend.title = element_blank())

```

## Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```

**Placing the mappings in the `ggplot()` function applies them to every layer in that graph. My placing the `color = drv` mapping in `geom_point()`rather than in `ggplot()`, it tells R that the `geom_smooth()` layer should only be mapping the `x` and `y` aesthetics, as coded in the `ggplot()` function.**

### Corrected Graph 4

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y=hwy)) + 
  geom_point(mapping = aes(color = drv)) + 
  geom_smooth(se = F, color = "black") #se = F makes it so it won't show the error in the line of fit
```


## Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

Also, the x-axis labels were overlaping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?


```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45))
```
 
**`color` refers to the outline of the boxplot, while `fill` refers to the color of the box itself. You can add `vjust = 0.5` as an argument to the `element_text()` function to shift the x-axis labels down.** 

### Corrected Graph 5

```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, fill = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```