---
title: "What went wrong?"
author: "Edited by Julia Shangguan"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I try to fix the coding mistakes present in the examples.

### I loaded in the necessary packages according to Robert's instructions. 
```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```

### Graph Fail 1

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = city, y = hwy, color = "blue")) %>% 
  geom_point()

```
**Graph 1 Answer:** If you want to use 'mapping', it should be created by the aes function. I provided two different solutions, one that uses "mapping" and another that is more streamlined in which I directly called the dataset ("mpg") within the ggplot function. In both solutions, I added the geom_point layer with a ("+") to the ggplot function. Additionally, when I called str(mpg), I see that "city" doesn't exist, so I am assuming that "cty" was actually meant. 

*Graph 1 Solution #1*

```{r}
#library("ggplot2") #loaded library 
str(mpg) #checking the dataframes's structure
ggplot(data = mpg) +
  geom_point(mapping = aes(x = cty, y = hwy, color = "blue")) 
```

*Graph 1 Solution #2*

```{r}
ggplot(mpg, aes(x = cty, y = hwy, color = "blue")) + geom_point()
```

### Graph Fail 2

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

```

**Graph 2 Answer:** If you want to change the color of the points, the "color" argument should be outside the aes function. You assign variables to "color" within the aes function if you want to change the color of the graph according to levels of that variable. 

*Graph 2 Solution*

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

```

### Graph Fail 3

```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 2) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = c(5, 40))

```

**Graph 3 Answer:** Alpha changes the opacity. Setting alpha = 2 doesn't do anything because 100% opacity is already reached at alpha = 1. To increase point size, use the argument "size". Furthermore, to move the legend, use the theme function and the legend.position() argument. c(x,y) cannot be greater than (1,1) because (1,1) specifies the top right location of the graph. To remove elements from the graph, set "element_blank()" in theme() elements; see below. To remove the legend entirely, add layer: theme(legend.position = "none")

*Graph 3 Solution*

```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 2) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = c(0.6, .8), legend.title=element_blank()) 
  # + theme(legend.position = "none") #to remove legend
```

### Graph Fail 4

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```

**Graph 4 Answer:** Geom_smooth is creating a line for each level of "drv" because the data has been grouped by drv levels. If just one line is wanted for all the data points, remove the color argument. 

*Graph 4 Solution*

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(se = F) 
```


### Graph Fail 5

```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45))
```

**Graph 5 Answer:** To make the box one color, use the "fill" argument. To move the axis label, I used argument "vjust" to increase spacing between the x labels and ticks. 

*Graph 5 Solution*
```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, fill = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))
```

