---
title: "What went wrong?"
author: "Robert Gruener"
date due: "7/13/2020"
output: github_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

## HW02 Part A

In this document, I will add some examples of some coding mistakes, it is up to you to figure out why the graphs are messing up. 

### First load packages

It is always best to load the packages you need at the top of a script. It's another common coding formatting standard (like using the assignment operator instead of the equals sign). In this case, it helps people realize what they need to install for the script and gives an idea of what functions will be called. 

It is also best coding practice to only call the packages you use, so if you use a package but end up tossing the code you use for it, then make sure to remove loading it in the first place. For example, I could use `library("tidyverse")` but since this script will only be using ggplot2, I only load ggplot2.

```{r load libraries}
library("ggplot2")
library("magrittr") #so I can do some piping
```




### Graph Fail 1

What error is being thrown? How do you correct it? (hint, the error message tells you)

```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(mapping = aes(x = city, y = hwy, color = "blue")) %>% 
  geom_point()

```
### Graph Fail 1 (CORRECTED)
# first argument of ggplot is the dataset, 'city' variable is actually cty, and to add a geom_point layer, use a '+'.
```{r}
data(mpg) #this is a dataset from the ggplot2 package

mpg %>% 
  ggplot(data = mpg, mapping = aes(x = cty, y = hwy, color = "blue")) +
  geom_point()

```




### Graph Fail 2
Why aren't the points blue? It is making me blue that the points in the graph aren't blue :`(
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))

```
### Graph Fail 2 (CORRECTED)
# color goes outside of aes because it is not conveying info about the data.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

```




### Graph Fail 3
Two mistakes in this graph. First, I wanted to make the the points slightly bolder, but changing the alpha to 2 does nothing. What does alpha do and what does setting it to 2 do? What could be done instead if I want the points slightly bigger? 

Second, I wanted to move the legend on top of the graph since there aren't any points there, putting it at approximately the point/ordered pair (5, 40). How do you actually do this? Also, how do you remove the legend title ("class")? Finally, how would you remove the plot legend completely?
```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), alpha = 2) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = c(5, 40))

```
### Graph Fail 3 (CORRECTED)
# alpha values range from 0 to 1, or transparent to opaque, modifying the transparency of the data points. If you want the points to be be slightly bigger you should set shape to a higher value instead.
#You can change legend location through the theme elements, specifying general sections of the graph or specific coordinates. In order to remove the legend completely you would use the following layer: 'theme(legend.position = "none")
```{r}
mpg %>% 
ggplot() + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class), size = 2) + 
  theme(legend.direction = "horizontal") + 
  theme(legend.position = (c(5, 40)) +
  theme(legend.title = element_blank())

```




### Graph Fail 4
I wanted just one smoothing line. Just one line, to show the general relationship here. But that's not happening. Instead I'm getting 3 lines, why and fix it please?

```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```
### Graph Fail 4 (CORRECTED)
#any aesthetics added to the ggplot applies to every subsequent layer. Moving the 'color = drv' to the geom_point layer allows for the desired data representation.
```{r}
mpg %>% 
ggplot(mapping = aes(x = displ, y = hwy)) + 
  geom_point(aes, color = drv) + 
  geom_smooth(se = F) #se = F makes it so it won't show the error in the line of fit
```




### Graph Fail 5
I got tired of the points, so I went to boxplots instead. However, I wanted the boxes to be all one color, but setting the color aesthetic just changed the outline? How can I make the box one color, not just the outline? 

Also, the x-axis labels were overlaping, so I rotated them. But now they overlap the bottom of the graph. How can I fix this so axis labels aren't on the graph?


```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, color = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45))
```
### Graph Fail 5 (CORRECTED)
#In order to color the boxplots, you want to use fill not color. In order to readjust the x axis, use vjust?
```{r}
ggplot(data = mpg, mapping = aes(x = manufacturer, y = cty, fill = manufacturer)) + 
  geom_boxplot() + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.7))
```


